The need for continuous-use medications has become increasingly common, especially with the increase in the population's longevity.
Aging also brings with it more common problems related to vision, especially presbyopia, which can cause difficulty in reading.
These factors together can bring about a new problem, where patients confuse medication packaging because they are visually similar.
This work proposes a system capable of identifying and providing information about a medication, through the textual elements of the packaging, using computer vision.
To this end, a system was built in Python that receives an image file and reads the text, using different color codes for this image, a method that has proven effective for identifying the terms in the image.
If terms are found, the system classifies them and searches for them in \emph{Anvisa}'s \emph{Bulário Eletrônico}, which provides medicine leaflets, and, in the case of a valid response, loads the medicine leaflet file.
To test this system, an image bank with photos of medications was built, with approximately \num{1200} images.
During development, problems were noted with online access to the \emph{Bulário Eletrônico} portal, which is inaccessible at certain times of the day.
Problems were also noted related to the orientation of the text in the images, where it was necessary to adjust some images for correct reading.
The accuracy of the system for reading all or part of the terms of interest was just over \SI{80}{\percent} of the image bank, and of these terms, it was completely or partially successful in finding the file in more than \SI{85}{\percent} of the cases.
These results were better than the approximately \SI{26}{\percent} of partial or correct readings achieved by a similar system that does not use different color codes, which shows the gain involved in performance through this method.

\paragraph*{\textit{Keywords:}} \emph{Anvisa}; \emph{Bulário Eletrônico}; Assistive Technology; Digital Image Processing; Computer Vision; Optical Character Recognition; Python.
